The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-12-01 ms.Rmd
Update to thte feng example - in particular the output figure.

```{r fengworkflow, eval = TRUE, dpi = 600, fig.show = "hide", results = "hide", message = FALSE, fig.height = 9, fig.width = 9}
FengPapes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = PrintMap(points = FALSE,
                                 threshold = 0.05))
```

This module plots a static map of the predicted distribution, and the underlying data.
This map is shown in Figure 2A.
The resulting workflow contains all the code required to re-run the workflow, the input data and the results of executing each module.
The object `FengPapes` could therefore be saved as a binary file and shared as a reproducible representation of this research.

@@

```{r combinefengupdate, eval = TRUE, echo = FALSE, dpi = 600, fig.show = "hide", fig.height = 4.5, fig.width = 4.5}
# combine the static and interactive maps and first effect plot

# load both images
r_map1 <- brick('figs/fengworkflow-1.png')
r_map <- brick('figs/interactive_map.png')
r_resp <- raster('figs/fengChangeWorkflow-1.png')
r_resp <- brick(r_resp, r_resp, r_resp)

@@

# add a panel letter
mtext(text = 'C',
        side = 3,
        line = -1.5,
        adj = 0)

>>>>

```{r fengworkflow, eval = TRUE, dpi = 600, fig.show = "hide", results = "hide", message = FALSE, fig.height = 9, fig.width = 9}
FengPapes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
           covariate = Bioclim(extent = c(-130, -20, -60, 60),
                               layers = c(1:4, 6, 9, 10, 12, 15)),
           process = Chain(Clean, 
                           MESSMask,  
                           Background(n = 10000,
                                      bias = 200), 
                           Crossvalidate(k = 5)),
           model = MaxEnt,
           output = PrintMap(points = FALSE,
                             threshold = 0.05,
                             xlim = c(-130,-70),
                             ylim = c(20, 50)))

This workflow plots a static map of the predicted distribution, and the underlying data.
This map is shown in Figure 2A and corresponds to figure 3 in @Feng2015.
The resulting workflow contains all the code required to re-run the workflow, the input data and the results of executing each module.
The object `FengPapes` could therefore be saved as a binary file and shared as a reproducible representation of this research.

@@

```{r combinefengupdate, eval = TRUE, echo = FALSE, dpi = 600, fig.show = "hide", fig.height = 4.5, fig.width = 4.5}
# combine the static and interactive maps and first effect plot
# load both images
r_map1 <- brick('figs/fengworkflow-1.png')
r_map <- brick('figs/interactive_map.png')
r_resp <- raster('figs/fengChangeWorkflow-1.png')
r_resp <- brick(r_resp, r_resp, r_resp)

@@

# add a panel letter
mtext(text = 'C',
        side = 3,
        line = -1.5,
        adj = 0)  
```
